Final Model Analysis

### 2017-08-26 model fitting/final_model.Rmd
calibration/validation with rms and pec package

```{r, echo = FALSE}
# cross validation plan with k = 5
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

@@

  train[["predictions"]] <- exp(predict(model, type = "lp"))
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

@@

@@

x$predictions <- predict(model, type = "lp")

@@

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics # metrics on the full data set are similar to the metrics from cross validation
```

@@

# using different function
pec::predictSurvProb(model, newdata = test1[1:3,], times = c(0.5, 1, 10))

# plot prediction error curves, calibration plots, c index, fix cv function, plot predicted survival curve ?? 
# turn this into a function 
```

>>>>

```{r, cross validation plan, echo = FALSE}
# cross validation plan with k = 5
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

@@

  train[["predictions"]] <- exp(predict(model, type = "lp"))
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

@@

```{r, echo = FALSE}
# validation and calibration with rms package

valmodel <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + gratitude + prior_effort + weekday + strat(ampm) + sqrt(avg_tag_score) + poly(text_length, 2) + rcs(device_length, 5) + rcs(avg_tag_length, 4) + rcs(newline_ratio, 4), data = x, x = TRUE, y = TRUE, surv = TRUE, time.inc = 0.5, dxy = TRUE)

validation <- rms::validate(calmodel, method = "crossvalidation", B = 100, bw = F, dxy = TRUE, u = 0.5)
validation
# output: 
# Dxy = Somers' Dxy (2 ∗ (C − 0.5), where C is the concordance probability)
# R2: RN2 index
# Slope: Calibration slope (slope of predicted log odds vs true log odds) optimism value is a value of overfitting
# D: Discrimination index — likelihood ratio χ2 divided by the sample size
# U: Unreliability index — unitless index of how far the logit calibration curve intercept and slope are from (0, 1)
# Q: Logarithmic accuracy score - scaled version of the log-likelihood achieved by the predictive model
# g: g index (?)

# validate the model for calibration accuracy in predicting probability at 0.5 hours 
calibration <- rms::calibrate(calmodel, method = "crossvalidation", B = 100, bw = FALSE, u = 0.5)
calibration
plot(calibration)
# predicts and calibrates at 0.5 hours for each iteration of the bootstrap
# plot gives mean absolute error in predictions, mean squared error, and the 0.9 quantile of the absolute error
# error =  difference between the predicted values and the corresponding bias-corrected calibrated values

@@

x$predictions <- exp(predict(model, type = "lp"))

@@

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics # metrics on the full data set are similar to the metrics from cross validation
```

##### Getting estimated survival probabilities

@@

# using different function
pec::predictSurvProb(model, newdata = test1[1:3,], times = c(0.5, 1, 10))
```
